Supernova Host Galaxies in the Dark Energy Survey: III. The Evolving Galactic Rate of Type Ia Supernovae

### 2020-12-17 draft.tex
Updates from Overleaf

\section{Method \label{sec:method}}

@@

\subsubsection{Galaxy properties \label{subsubsec:properties}}

@@

\begin{figure}
\includegraphics[width=0.5\textwidth]{figs/mass_hist_log.png}
\caption{Distribution of the stellar mass of the field galaxies used in the analysis. The distribution is well desribed by a Schechter function.
\label{fig:log_mass_field}}
\end{figure}

\section{Incompleteness corrections \label{sec:incompleteness}}

@@

\section{Rates as a function of host galaxy properties \label{sec:rates}}

>>>>

@@

\begin{figure}
    \centering
    \includegraphics[width=.5\textwidth]{figs/mass_hist_sn_field_BC03.png}
    \caption{Distribution of the stellar mass of the SN host and field galaxies used in the analysis. }
    \label{fig:mass_hist_hosts_field}
\end{figure}

\subsection{Galaxy properties \label{subsec:properties}}

@@

\begin{figure}
    \centering
    \includegraphics[width=0.5\textwidth]{figs/mass_hist_log_BC03.png}
    \caption{Distribution of the stellar mass of the field galaxies used in the analysis. The distribution is well described by a Schechter function.
    \label{fig:log_mass_field}}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=.5\textwidth]{figs/rate_vs_mass_DTD_fit_beta_norm.png}
    \caption{The rate per galaxy of SNe Ia as a function of stellar mass. The blue lines indicate the best fitting model based on a $t^{\beta}$ power law DTD convolved with SFHs based on the \citet{Childress2014} model}
    \label{fig:rate_fit}
\end{figure}
\section{Incompleteness corrections \label{sec:incompleteness}}

@@

\begin{figure*}
    \centering
    \includegraphics{}
    \caption{Caption}
    \label{fig:my_label}
\end{figure*}

\section{Modeling the rate of type Ia supernovae \label{sec:method}}

The result of our toy model is shown in Fig. \ref{fig:SFHs}

\section{Results \label{sec:rates}}
